\documentclass[letterpaper,11pt]{article}

\def\theme{sitegreen}
\usepackage{simplecv}

\begin{document}

\cvheading{Robert Kuska}{Software Engineer}{
  Brno, Czech Republic\\
  \email{robert@kuska.xyz}\\
  \website{robert.kuska.xyz}
}

\cvsection{Skills}

\cvtext{
Golang, Python, Ruby, PostgreSQL, Cassandra, ScyllaDB, backend engineering,
monitoring, leadership, software architecture, microservices, Docker, Vim,
Linux
}

\cvsection{Experience}

\cvjob
    {Apropos}
    {July 2024 -- Present}
    {Founding Engineer}
    {Remote, HQ in New York City, USA}
  {
    Created the backend around Python and Go, including asynchronous data
    pipelines communicating over Google Cloud Pub/Sub. Worked on scraping,
    data processing, LLM-backed workflows, and rapid prototyping.
  }

\cvjob
    {Qonto}
    {January 2020 -- July 2024}
    {Staff Software Engineer}
    {Remote, HQ in Paris, France}
  {
    Worked on the Ledger team, focused on bookkeeping operations and
    resource-intensive transaction processing. Helped migrate synchronous
    HTTP flows to an event-driven architecture using Kafka.
    \cvparagraph{
    Led the internal Golang coding academy, mentoring engineers joining Go
    backend teams. Drove scalability work through batch optimization,
    database load reduction, profiling, benchmarking, and capacity planning.
    }
  }

\cvjob
    {Kiwi.com}
    {November 2015 -- December 2019}
    {Technical Lead}
    {Brno, Czech Republic}
  {
    Started as a Senior Software Engineer in the Booking tribe, working on
    backend systems for booking creation and payment fraud detection, including
    on-call ownership for critical systems.
    \cvparagraph{
    Later led Kiwi.com's first Go backend team in the Search tribe. Helped
    migrate flight storage from Cassandra to ScyllaDB, a distributed database
    deployment across three data centers with seven nodes each, handling around
    700k writes and 500k reads per second.
    }
    \cvparagraph{
    Read more:
    \link{https://www.scylladb.com/users/case-study-kiwi-takes-flight-with-scylla/}
      {ScyllaDB customer story}
    }
  }

\cvjob
    {Red Hat}
    {April 2013 -- April 2016}
    {Software Engineer}
    {Brno, Czech Republic}
  {
    Worked on the user experience team maintaining CPython within Fedora and
    RHEL. Helped drive the transition to Python 3 as the default in Fedora 23
    and co-authored PEP 493, which provided HTTPS verification migration tools
    for Python 2.7.
  }

\cvsection{Education}

\cveducation
    {Masaryk University}
    {2013}
    {Faculty of Informatics, BSc}
    {Brno, Czech Republic}
  {
    Thesis: \textit{Methods of automatic testing in Python language}.
    \cvparagraph{
    The thesis covers testing in Python, usage examples for common freely
    available test libraries, libraries for creating fake objects, and a
    performance comparison of selected libraries applied to the MCC project.
    }
  }

\cvsection{Talks}

\cvtalk
    {PyCon CZ: Bits and bytes of Python memory management}
    {2018}
    {\link{https://cz.pycon.org/2018/programme/detail/talk/12/}
      {cz.pycon.org/2018/programme/detail/talk/12/}}

\cvtalk
    {PyCon CZ: Feed your code to coala}
    {2016}
    {\link{https://pyvideo.org/pycon-cz-2016/feed-your-code-to-coala.html}
      {pyvideo.org/pycon-cz-2016/feed-your-code-to-coala.html}}

\end{document}
